
\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
% pkg: url, href

\title{Josceleton}
\author{A Gesture-Based Application Framework}

\begin{document}

\maketitle
%\tableofcontents

\section{Target Setting}
description
mission stmt
FOTOs von skelet zeugs
quer-referenz pulse project

= gesture-based interface.


\section{Nerdy Stuff}

\subsection{Technology Stack}

Kinect, OpenNI Framework (``Natural Interaction'' Framework; opensourced by PrimeSense; performs ``skeletonization''), NITE (is a toolbox to allow application to build flows base don the user's hands movement and is built upon OpenNI), OSCeleton (an OSC proxy that broadcasts skeleton data from the Kinect middleware as OSC messages, which is standard format for real time messaging similar to midi), Java OSC, Josceleton, YOU

? PrimeSense sensore modul?

3D kubus, wie koordinaten daherkommen.

\subsection{Software Architecture}

Module, Klassen wie sie zusammenarbeiten; strikte API/impl trennung, Codesamples, Diagrams \ldots

zb: Connector, rohe ConnectionListener joint/user messages; was macht UserService (artificial login), unterschied MotionStream und ContinuousMotionStream

Stuff: maven (build infrastructure, release-app), guice, coding policies (100\% coverage, several -build enforced- code quality plugins), \ldots aop/jcontractor

screenshot von prototypen + papierprototypen wie es aussehen soll.


\section{Roadmap}

\begin{itemize}
	\item Version 1.0: MIDI Support for Pulse project finished; several prototypes.
	\item Version 2.0: Piano Sample App and Console App finished; some gestures available.
	\item Version 3.0: Application Framework; many gestures, positions and stream based motion data.
\end{itemize}

See Mantis.

Visions \ldots lego mindstorm extension, 3d visualisation


\subsection{Supported Gestures}

Gestures: HitWall, Relative
Positions: 
Streams: 
Misc: Callibration

\section{Appendix}

\subsection*{Glossary}

Joint
Motion(Stream)



\subsection*{Links}

\begin{tabular}{ll}
	foo was & http://osceleton.com \\
	faa & http://sensebloom.com
\end{tabular}


\end{document}
